Software Citation Principles

### 2016-07-22 sc-principles/software-citation-principles.tex
adding a comment
adding response to comment

\niemnote{this seems the same as use case 1}
The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.

>>>>

\niemnote{this seems the same as use case 1} \katznote{I thought it was the same as 6}
\niemnote{6 is about reproducing, while this seems to be writing a software paper}
The research wants to publish about a version of software they have produced.
A key part of this use case is to be able to connect the given narrative to a specific version of the software in questions and connect that in large story.
